\include{preamble}
\include{begin}

\chapter*{Abstract}
%\noindent % abstract text

Superconducting transition temperature ($T_{c}$) is one of the most important quantities of superconductors. 
Since the discovery of superconductors, theories and methods which can predict the $T_c$ from
first-principles have been energerically studied. Recently, the density functional theory for 
superconductors (SCDFT) and related numerical scheme to calculate $T_c$ has been developed. Applying the recently 
developed scheme, $T_c$s for various kinds of phonon-mediated conventional superconductors can be 
reproduced from first-principles in sufficient accuracy.

It has been argued found that the pairing mechanism of recently discovered high-$T_c$ 
superconductors, e.g. Fe-based superconductors and cuprates, is not dominated by the electron-phonon 
interaction. Instead of electron-phonon interaction, the effect of spin fluctuations has been suggested
as the possible pairing mechanism in these unconventional superconductors. According to this 
consideration, an extended SCDFT-based method including the effect of spin fluctuations has been 
developed recently.

On the other hand, the effect of spin fluctuations on $T_c$ is also appreciable in phonon-mediated conventional
superconductors. Even in many metals in which electrons are nearly homogeneously distributed, ferromagnetic fluctuations
are driven by the Pauli exchange effect and they suppress the phonon-mediated singlet pairing. So far, this effect on 
$T_c$ of conventional superconductors has scarcely been studied from first-principles.

In this thesis, we apply the recently developed extended SCDFT scheme to some elemental metals, V, Nb and Al 
and study the $T_c$ suppression due to spin fluctuations for these materials. As a result,
$T_c$ of V is reduced from 17.8K to 8.3K, and that of Nb is reduced from 11.1K to 8.9K by including
the effect of spin fluctuations and the agreement between experimental data is improved for both 
metals. On the other hand, $T_c$s of Al with and without the effect of spin fluctuations are 1.4K.
These difference of
the effect of spin fluctuations is related to the magnitude of electronic localization.

These calculation results indicate that the extended SCDFT-based scheme enables us to calculate  
$T_c$ for various kinds of phonon-mediated superconductors accurately than previous one. Our 
accomplishment is helpful to design novel superconductors theoretically.




\clearpage

\include{end}
