\include{preamble}
\include{begin}
%
% Contents
%
\chapter{Introduction}



%%%%%%%%%%%%%%%%%%%%%   PURPOSE OF THIS STUDY %%%%%%%%%%%%%%%%
\section{History of studies on conventional superconductors: Overview}
Since its discovery in 1911\cite{Onnes1911}, superconductivity has been one of the most fascinating
subject in the condensed matter physics. One of the characteristic properties of superconductors is
the zero resistivity and another is the Meissner effect\cite{Meissner1933}.
The latter means that bulk superconductors exclude the magnetic flux.
In 1950, Maxwell\cite{Maxwell1950} and Reynolds\cite{Reynolds1950} independently discovered the 
isotope effect for Hg,
%
\begin{equation}
	T_{c} \propto M^{-\alpha}, \alpha \approx 0.5,
	\label{eq:isotope}
\end{equation}
%
where $T_c$ is the superconducting transition temperature and $M$ indicates the mass of ion.
Although many results were presented experimentally soon after the discovery of superconductors,
it took a nearly half century until a successful microscopic theory for superconductors is presented.

In 1950, Fr\"{o}hlich\cite{Froehlich1950} demonstrated that the electron-phonon interaction induces the
effective attractive interaction between electrons. This idea is consistent to the Meissner effect.
Based on this idea that the electronic condensation originates from the electron-phonon interaction, 
Bardeen, Cooper and Schrieffer(BCS)\cite{BCS1957} successfully constructed the microscopic 
theory by introducing the electronic many-body wave function which consist of electron pairs named as
Cooper pairs\cite{Cooper1956}. According to the BCS theory, $T_c$ is written as
%
\begin{equation}
	T_{c} \propto \omega\exp \left( -\frac{1}{N(0)V} \right),
	\label{eq:TcBCS}
\end{equation}
%
where $\omega, N(0), V$ is the typical phonon frequency, the density of states at the Fermi energy, 
and the characteristic attractive interaction between electrons respectively.

In the BCS theory, the effective interaction between electrons is only assumed to be attractive and
the detail of the interaction is not studied.
In the late 1950s and 1960s, the detail of the phonon-mediated pairing interaction, namely the 
dynamical strucure of the electron-phonon interactinon, is studied by means of the Green's function 
formalism\cite{Migdal1958,Nambu1960,Eliashberg1960,Morel1962,Schrieffer1964,Scalapino1966}. 
This theory is called as Migdal-Eliashberg(ME) theory.
McMillan\cite{McMillan1968} solved the Eliashberg equation analytically and numerically, and derived
the equation which describe $T_c$ with a simple analytic funcion. Later, the McMillan's equation
was revised by Allen and Dynes\cite{AllenDynes} and the resulting formula is
%
\begin{equation}
	T_c = \frac{\omega_{\rm ln}}{1.2} \exp \left( -\frac{1.04(1+\lambda)}
	{\lambda-\mu^{\ast}(1+0.62\lambda)} \right),
	\label{eq:MAD}
\end{equation}
%
where $\omega_{\rm ln}$ indicates the logarithmic average of the typical phonon frequencies and
$\lambda$ is the dimensionless electron-phonon coupling. Finally, $\mu^{\ast}$ is the effective Coulomb
parater defined as
%
\begin{equation}
	\mu^{\ast} \equiv \frac{\mu}{1 + \mu \ln \left[ \frac{E_c}{\omega_{\rm ph}} \right]},
	\label{eq:mustar}
\end{equation}
%
where $\mu$ is the dimensionless Coulomb interaction parameter defined as the product of the density
of states at the Fermi energy and the averaged screened Coulomb interaction, $E_c$ is the
electronic band width and $\omega_{\rm ph}$ is the typical phonon frequency.



\include{end}
