\include{preamble}
\include{begin}
%
% Contents
%
\chapter{Conclusion}
\label{conclusion}

\section{Summary}
In this thesis, we implemented source codes to compute the interaction mediated by spin fluctuations
following the recently developed formalism\cite{Essenberger2014}
and explored the effect of spin fluctuations on superconducting transition temperatures ($T_c$)
of V, Nb and Al from first principles by using the extended SCDFT scheme including the effect of 
spin fluctuations\cite{Essenberger2014}.
As a result, it is confirmed that the effect of spin fluctuations commonly
reduces the $T_c$ of transition metals. 
For V having $3d$ electrons, $T_c$ with the effect of spin fluctuations is 8.3K, while that 
without this effect is 17.8K.
For Nb having $4d$ electrons, $T_c$ with the effect of spin fluctuations is 8.9K, while that 
without this effect is 11.1K.
The agreement of calculated $T_c$s with the experimental values is improved for both of these 
two materials. On the other hand, the $T_c$ reduction is not observed for Al.
According to these results, it can be deduced that the reduction of $T_c$ due to spin fluctuations
is related to the magnitude of the electronic localization.

\section{Future issues}

\begin{description}
	\item[Formalism] \mbox{}\\
We found that the recently developed formalism has a problem with respect to the frequency dependence
of the effective interaction mediated by spin fluctuations. Therefore, we {\it ad hoc} neglected
one problematic term $f^{\rm xc}$. 
There are some possible causes of the problematic term. One direct cause is the adiabatic 
approximation for $f^{\rm xc}$. This approximation makes $f^{\rm xc}$ frequency-independent(Chapter 
\ref{application}).
Other possible causes are the choice of the initial self-energy (see (\ref{eq:localapp})) and 
the fact that we used the particle-hole propagator in order to take into account the effect of
spin fluctuations. In practice, these assumptions are inevitable to avoid the numerical difficulty 
to handle four-point functions. Some approximations which can handle the effect of spin 
fluctuations with two-point functions without involving the problem of frequency dependence may 
overcome this difficulty.

As noted in \ref{kernelSF}, we do not take into account the mass renormalization 
originating from spin fluctuations $\mathcal Z^{\rm SF}$ in this study.
The development of numerical algorithms to compute this term with a good accuracy is also required.

\item[Application] \mbox{}\\
	In this thesis it is shown that $T_c$ of some materials are estimated more accurately by 
	including the effect of spin fluctuations from first principles. 
	In principle, this extension can be applied to any 
	kind of superconductors because the spin fluctuations are quite general phenomena.
	Although this extended scheme is first developed in order to study the pairing mechanism in 
	Fe-based superconductors and already applied to FeSe\cite{Essenberger2016},
	this extended scheme is also helpful to understand the mechanism of certain 
	high-$T_c$ superconductors.


\end{description}

\include{end}
